%-------------------------
% Resume in Latex
% Author : CJ Coleman-Benjamin
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape CJ Coleman-Benjamin} \\ \vspace{1pt}
    \small 07940477239 $|$ \href{mailto:cjcolemanbenjamin@gmail.com}{\underline{cjcolemanbenjamin@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/cj-coleman-benjamin-144433222/}{\underline{LinkedIn}} $|$
    \href{https://github.com/CJ-Coleman}{\underline{GitHub}} \\ \vspace{2pt}
    \normalsize \href{https://cjcolemanb.github.io/}{\underline{Portfolio Website}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Leeds}{Leeds, West Yorkshire}
      {BSc in Computer Science with Artificial Intelligence}{Oct. 2023 - Aug. 2025}
      \begin{itemize}
          \item In the process of transferring universities, due to job opportunities in London
          \item On track for a 2:1, Key Modules:
          \begin{itemize}
              \item Software Engineering Project (88\%), Object Oriented Programming (77\%), Procedural Programming (75\%)
          \end{itemize}
      \end{itemize}
    \resumeSubheading
      {Royal Russell School}{Croydon, London}
      {Achieved AAB at A level, and 4 9s at GCSE}{Sep. 2016 - Aug. 2023}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
\resumeSubheading
      {DeviceLogger}{October 2025}
      {Streatham and Clapham School}{London}
      \resumeItemListStart
        \resumeItem{Developed, implemented, and deployed a system to standardise the process of loaning devices for hundreds of pupils and staff members.}
        \resumeItem{The system tracked device inventory, managed check-out/check-in, and maintained loan history, improving efficiency and accountability.}
      \resumeItemListEnd
    \resumeSubheading
      {Full Stack Auction Website}{April 2025 - June 2025}
      {University of Leeds}{Leeds, West Yorkshire}
      \resumeItemListStart
        \resumeItem{Within a team of 6, developed a full stack flask-based website centered around auctioning. Includes payment integration, proper use of a database (SQLite), as well as proper redirection for error handling.}
\resumeItem{Explored ways to integrate application support, as opposed to exclusively website-based.}
\resumeItem{Was also the scrum master for this project, as well as a lead planner. Followed Agile planning for the website.} \resumeItemListEnd

    \resumeSubheading
          {AI-based Report}{April 2025 - June 2025}
          {University of Leeds}{Leeds, West Yorkshire}
          \resumeItemListStart
            \resumeItem{Created an individual report based on the adoption of external languages within social media (specifically between native English, as well as native Japanese speakers).}
    \resumeItem{Used Python, as well as libraries such as Pandas, NumPy, and Matplotlib, in addition to AI generative tools such as DeepSeek to web-scrape information to create graphs and tables of information for further analysis.} \resumeItemListEnd
    
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {IT Technician}{September 2025 - Present}
      {Streatham and Clapham School (GDST)}{London}
      \resumeItemListStart
        \resumeItem{Provided first-line IT support to staff and students, troubleshooting hardware (desktops, laptops, printers) and software issues.}
        \resumeItem{Assisted in maintaining classroom AV equipment (projectors, smart boards) and ensuring network connectivity.}
        \resumeItem{Managed user accounts and supported the deployment of new software across the school's network.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Retail Assistant}{October 2021 - February 2022}
      {Mark's \& Spencer}{Merton, London}
      \resumeItemListStart
        \resumeItem{Worked as a Retail assistant for Mark's \& Spencer in the Merton branch in london. Achieved extremely positive feedback from customers, as well as breaking in-store records for quantity of positive reviews from customers.}
      \resumeItemListEnd

    \resumeSubheading
      {President of General Assembly MUN}{October 2022}
      {Royal Russell School}{Croydon, London}
      \resumeItemListStart
        \resumeItem{Was a President of General Assembly for RRS40MUN, working in a small team of other students to hold a 5 day debate conference from schools internationally, including over 200 students on campus at any time.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C++, SQLite, JavaScript, HTML/CSS, MarkDown, Microsoft Office Tools} \\
     \textbf{Frameworks}{: React,  Flask} \\
     \textbf{Developer Tools}{: Git, TravisCI, VS Code, Visual Studio, PyCharm} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, werkzeug, Tkinter}
    }}
 \end{itemize}


%-----------ADDITIONAL SKILLS--------------------------------
\section{Additional Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English (native), Japanese (intermediate, N4 level), French (intermediate).} \\
     \textbf{Frameworks}{: React,  Flask} \\
     \textbf{Skills and Hobbies}{: Playing volleyball, Listening to music, gaming, video development, building computers and keyboards, etc.} \\
    }}
 \end{itemize}
\end{document}